On Secure Delegation of SampBQP with a Classical Client

### 2020-03-09 bqp-rewrite.tex
Write proof draft for blindness compiler soundness

	Using $\Pi=(P, V)(x)$ from above, we now define the protocol $\Piblind=(P, V(x))$ as follows:

@@

	Verifier's input: $x$
	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
			and encrypts $\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_0, \ctx{v_1}{1}, \ctx{x}{1})$.
			It sends $\ctx{p_1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
				and generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
				and produces encryptions $\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
			\item $\Pblind$ updates its state to use the new $\QHE$ key by
				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
				then homomorphically decrypting the old encryption by
				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
				It then applies the next-message function of $\Pi$, generating
				$(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v_t}{t}, \ctx{st_{P, t-1}}{t})$.
				It sends $\ctx{p_t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p_T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

\begin{theorem}
	For all cheating prover $\Pblind^*$ of $\Piblind$, there exists a cheating prover $P^*$ of $\Pi$ s.t. for all input $x$, the output distributions of $(\Pblind, \Vblind(x))$ and $(P, V)(x)$ are negligibly close.
\end{theorem}
\begin{proof}
	TODO
\end{proof}

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument as below:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T$ hybrids...
\end{proof}

>>>>

	Using $\Pi=(P, V)(x)$ from above, we define the protocol $\Piblind=(P, V(x))$ as follows:

	Verifier's input: $x$

@@

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
			and encrypts $\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
			It sends $pk_1$, $\ctx{x}{1}$, and $\ctx{v_1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$
			by evaluating $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v_1}{1}, \ctx{x}{1})$.
			It sends $\ctx{p_1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p_{t-1}}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
				and produces encryptions $\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
				It sends $pk_t$, $\ctx{v_t}{t}$, and $\ctx{sk_{t-1}}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$
				by first refreshing the $\QHE$ key that encrypts its states by
				first encrypting it under the new key by $\ctx{st_{P, t-1}}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st_{P, t-1}}{t-1}))$,
				then homomorphically decrypting the old encryption under the new key by
				$\ctx{st_{P, t-1}}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1, t})$.
				It then applies the next-message function of $\Pi$, generating
				$(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v_t}{t}, \ctx{st_{P, t-1}}{t})$.
				It sends $\ctx{p_t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p_T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

\def\Pstar{P^*}
\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}

\begin{theorem}
	For all cheating prover $\Pblindstar$, there exists a cheating prover $\Pstar$ s.t. for all input $x$, the output distributions of $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{theorem}
\begin{proof}
	We define $\Pstar$ so that on $\cPstar{1}$ it generates
	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
	$\ctx{x}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v_1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
	It then runs $(\ctx{p_1}{1}, \ctx{st_{P, 1}}{1})\leftarrow\cPblind{1}(\ctx{v_1}{1}, \ctx{x}{1})$.
	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p_1}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, 1}}{1}$ and $sk_1$.
	Then, on the rest of the $\cPstar{t}$ rounds, $\Pstar$ generates
	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
	$\ctx{v_t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk_{t-1}}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
	It then runs $(\ctx{p_t}{t}, \ctx{st_{P, t}}{t})\leftarrow\cPblind{t}(\ctx{v_t}{t}, \ctx{sk_{t-1}}{t}, \ctx{st_{P, t-1}}{t-1})$.
	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p_t}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st_{P, t}}{t}$ and $sk_t$.

	By construction, the experiments $(\Pblindstar, \Vblind(x))$ and $(\Pstar, V)(x)$ are identical.
\end{proof}

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T$ hybrids...
\end{proof}
